Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2025-01-30 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
xxxxx

@@

@@

### self-evaluations of disruption prevention and management competencies (5 classroom management items + 3 self-developed, 8 presence items)
```{r self-eval_8-8, echo=FALSE, results='asis'}

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(
    Group = factor(Group, levels = c("Novice", "Expert")),
    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management", "Presence", "Overall"))  # Reorder scales
  ) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  ylim(0, 4) + 
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )

# Perform t-Tests for Each Scale
t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management", "Classroom Management")
t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")

# Calculate omega for Classroom Management
omega_cm <- calculate_omega_total(df_cm, "Classroom Management")

### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
# APA-Conform Table ------------------------------------------------------
omega_results <- tibble(
  Facet = c("Overall Evaluation", "Classroom Management", "Presence"),
  `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
)

>>>>

#################### Data Preparation ########################
df_aoi_sum <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    -contains("Disruptive_Person")
  ) %>%
  rowwise() %>%
  transmute(
    Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
    Participant,
    Duration_of_interval_min = Duration_of_interval / 60000,
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Number_fixation_min_mtu = Sum_number_fixation / Duration_of_interval_min,
    Avg_fixation_duration = Sum_duration_fixation / Sum_number_fixation
  ) %>%
  drop_na()

@@

### Self-evaluations of disruption prevention and management competencies (5 classroom management items + 3 self-developed, 8 presence items)
```{r self-eval_8-8, echo=FALSE, results='asis'}

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(
    Group = factor(Group, levels = c("Novice", "Expert")),
    `Scales Self-evaluation` = factor(`Scales Self-evaluation`, levels = c("Classroom Management + 3 Items", "Presence", "Overall"))  # Reorder scales
  ) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  ylim(0, 4) + 
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )

# # Create Dataset for Plotting with Overall Score Only -------------------------
# df_quest_long <- df_quest %>%
#   rowwise() %>%
#   transmute(
#     Group = Group,
#     `Overall` = round(mean(c(CM_01, CM_02, CM_03, CM_04, CM_05, CM_06, CM_07, CM_08, P_01, P_02, P_03, P_04, P_05, P_06, P_07, P_08), na.rm = TRUE), 2)  # Overall score only
#   ) %>%
#   ungroup()
# 
# # Plot Overall Mean Scores by Group ----------------------------------------------
# quest_plot <- df_quest_long %>%
#   mutate(
#     Group = factor(Group, levels = c("Novice", "Expert"))
#   ) %>%
#   ggplot(aes(x = Group, y = Overall, fill = Group)) +
#   geom_boxplot(outlier.shape = NA) +
#   geom_point(
#     size = 1,
#     alpha = 0.4,
#     position = position_jitter(seed = 1, width = 0.1, height = 0.1)
#   ) +
#   labs(x = "", y = "Overall Mean Score") +
#   ylim(0, 4) + 
#   scale_fill_brewer(palette = "RdBu") +
#   theme_cowplot() +
#   ggtitle("Overall Self-Evaluation Scores") +
#   theme(
#     plot.title = element_text(size = 25, face = "bold"),
#     legend.title = element_text(size = 20),
#     legend.text = element_text(size = 15),
#     axis.text.x = element_blank(),
#     axis.ticks.x = element_blank(),
#     axis.title.y = element_text(size = 20)
#   )
# 
# print(quest_plot)

# Perform t-Tests for Each Scale
t_test_all <- t_test_stats_long(df_quest_long, "Group", "Overall", "Overall Evaluation")
t_test_cm <- t_test_stats_long(df_quest_long, "Group", "Classroom Management + 3 Items", "Classroom Management + 3 Items")
t_test_presence <- t_test_stats_long(df_quest_long, "Group", "Presence", "Presence")

# Calculate omega for Classroom Management
omega_cm <- calculate_omega_total(df_cm, "Classroom Management + 3 Items")

### COMBINE RESULTS INTO AN APA-CONFORM TABLE ----------------------------
# APA-Conform Table ------------------------------------------------------
omega_results <- tibble(
  Facet = c("Overall Evaluation", "Classroom Management + 3 Items", "Presence"),
  `Omega Total` = c(omega_self_all, omega_cm, omega_presence)
)

@@
